\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-08-07 metatheory.tex
syntactical → syntactic
Add the part why we use predicative MLTT.

% Motivation of using QIIT
We start with the formulation of the syntax in the declarative style, which is based on the
formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT)~\cite{martin1982constructive}
given by~\citet{coquand2018canonicity}. 
% Thus we will omit a great deal of details about MLTT here
\YZ{What details are omitted?} 
We will mainly focus on the new facility that we introduced

@@

\subsection{Implementation Formalized as Syntactical Translation}

>>>>

% Motivation of using QIIT
We start with the formulation of the syntax in the declarative style, which is based on the
formalization of a predicative \textit{Martin-Lof Type Theory} (MLTT)~\cite{martin1982constructive}
given by~\citet{coquand2018canonicity}. We will mainly focus on the new facility that we introduced.

The reason we choose this version of predicative MLTT is mainly because it is simpler on the formulation and metatheoretical reasoning, easy to extend and is enough as a background for setting up the formalization of the key feature for our language, like overriding and inheritance about the families. Compared to a more complete Coq's formal foundation like \textit{Predicative Calculus of Cumulative Inductive Constructions}~\cite{timany2018cumulative}, our formulation lacks cumulativity (though our formulation still has multi-level universe) and impredicative universe (the \mintinline{Coq}{Prop : Type}). \YZ{
    What's the relation to the CIC underlying Coq, given that the implementation is a Coq plugin?
}\EDJreply{Add the comparison between this version of predicative MLTT and PCUIC. Please Check.}
% Thus we will omit a great deal of details about MLTT here

@@

\subsection{Implementation Formalized as Syntactic Translation}
